A neural coarse graining theory of consciousness/\newline Non-trivial Informational closure through neural coarse-graining as the Fundamental Informational Correlates of Consciousness

### 2019-04-23 Paper_neural_coarse_graining_of_consciousness.tex
Updates from Overleaf

@@

>>>>

	    Note that, the environment of a NTIC process in the nerual system includes not only the\todo{Werite this}

@@

		\subsection{Discuss items}
		\begin{ants}
		    @ Conscious

		    @ Boundary 
    		    @@ binocular rivalry
    		    @@ Libet's experiment
    		    @@ Priming
    		    @@ Bistable perception
    		    @@ Perceptual overflow
    		    @@ Unconscious determinants of free decisions in the human brain
    		    @@ Threshold of unconscious to consciousness
    		    @@ Probabilistic information is always unconscious

		    @ Unconscious
